---
title: "1. Installing trackRcv"
author: "Simon Garnier"
vignette: >
  %\VignetteIndexEntry{z1_installing_trackRcv}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
knitr:
  opts_chunk:
    collapse: true
    comment: '#>'
---

## 1. Installing `trackRcv`

### 1.1. From CRAN

`trackRcv` is currently not available on CRAN.

### 1.2. From GitHub

You can install `trackRcv` and the rest of its dependencies by simply typing the following command in your R console:

```{r, eval=FALSE}
pak::pak("swarm-lab/trackRcv")
```

------------------------------------------------------------------------

## 2. Setting up `trackRcv`

Once the installation is complete, you will need to run the following command in your R console:

```{r, eval=FALSE}
trackRcv::install_cv()
```

Answer “Yes” to all the questions. This will create a dedicated Python virtual environment containing all the Python dependencies that `trackRcv` needs to run. This environment will not interfere with any other Python environments on your system, and it can be removed at any time by running the following command:

```{r, eval=FALSE}
trackRcv::remove_cv()
```

Once this is done, you can proceed to the next tutorial to learn how to use `trackRcv`.